Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-05-02 paper.tex
Add similarity matrix/DTW figure

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{sims_and_dtws.pdf}
  \caption{Audio and hash-based features and alignment for Billy Idol - ``Dancing With Myself'' (MSD track ID \texttt{TRCZQLG128F427296A}).
           (a) Normalized constant-Q transform of 7digital preview clip, with beat indices and semitones on the horizontal and vertical axes respectively.
	   (b) Normalized CQT for synthesized MIDI file.
	   (c) Hash bitvector sequence for 7digital preview clip, with pooled beat indices and Hamming space dimension on the horizontal and vertical axes respectively.
	   (d) Hash sequence for synthesized MIDI.
	   (e) Similarity matrix and DTW path (displayed as a white dotted line) for CQTs.
	   (f) Similarity matrix and DTW path for hash sequences.}
\end{figure*}
